---
title: "Assignment 10.3 Step 2 of Final Project"
author: "Basak Atanu"
date: 05-19-2022
output:
  
  pdf_document: default
---

# Data Preparation for Exploratory Data Analysis
```{r}
setwd("C:\\Users\\atanu\\Documents\\BellevueUniversity_MSDS\\DSC520\\Loan Defaulter Data")
default_fin <- read.csv("Default_Fin.csv")
head(default_fin)
```
### This data is related to defaulters, this gives individual's information like if the applicant is employed or not, their bank balance annual salary and if the application defaulted.
```{r}
setwd("C:\\Users\\atanu\\Documents\\BellevueUniversity_MSDS\\DSC520\\Loan Defaulter Data")
loan_data <- read.csv("loan_data.csv")
summary(loan_data)
```
### This dataset gives the loan details like the interest rate, fico of the customer, type of the loan, annual income along with fully paid or not flag.
```{r}
setwd("C:\\Users\\atanu\\Documents\\BellevueUniversity_MSDS\\DSC520\\Loan Defaulter Data")
application_data <- read.csv("application_data.csv")
summary(application_data)
```
### This data set is about loan application where Target field having 1 means the applicant have difficulty while paying for the loan and also have more than x day late payment.