---
title: "Assignment 10.3 Step 2 of Final Project"
author: "Basak Atanu"
date: 05-19-2022
output:
  
  pdf_document: default
---

# Data Preparation for Exploratory Data Analysis
```{r}
setwd("C:\\Users\\atanu\\Documents\\BellevueUniversity_MSDS\\DSC520\\Loan Defaulter Data")
default_fin <- read.csv("Default_Fin.csv")
head(default_fin)
```
### This data is related to defaulters, this gives individual's information like if the applicant is employed or not, their bank balance annual salary and if the application defaulted.
```{r}
setwd("C:\\Users\\atanu\\Documents\\BellevueUniversity_MSDS\\DSC520\\Loan Defaulter Data")
loan_data <- read.csv("loan_data.csv")
summary(loan_data)
```
### This dataset gives the loan details like the interest rate, fico of the customer, type of the loan, annual income along with fully paid or not flag.
```{r}
setwd("C:\\Users\\atanu\\Documents\\BellevueUniversity_MSDS\\DSC520\\Loan Defaulter Data")
application_data <- read.csv("application_data.csv")

```
### This data set is about loan application where Target field having 1 means the applicant have difficulty while paying for the loan and also have more than x day late payment.

### Below are the list of Questions, that we are planning to answer using this data.
## 1. What attributes affect loan default and what are some major reasons behind it?
## 2. Is there any co-realation between different attributes of loan default data and gereral loan data?
## 3. I think, Income having a direct effect on loan default, because low income could cause default for loan payment. is it true?
## 4. Can I predict if the loan will go to default if I have employment, annual salary and bank balance information?
## 5. Does high fico socre give lower interest retes for loan?.

```{r}
library(naniar)
miss_var_summary(default_fin)
miss_var_summary(loan_data)
miss_var_summary(application_data)
```
### application_data have sereral missing values so lets eleminate those columns which have more than 10% missing values.
```{r}
application_data <- application_data[ lapply( application_data, 
                                              function(x) sum(is.na(x)) / length(x) ) < 0.1 ]
miss_var_summary(application_data)
```
### lets eleminate the records that have missing values using the below command.

```{r}
library(tidyr)
application_data <- na.omit(application_data)
miss_var_summary(application_data)
```
### as missing data has been removed from the dataframe we can start analysis. I am using the corrplot to see the correlation matrix. 

```{r}
library(corrplot)
corrplot(cor(default_fin, method = c("spearman")))
```
### Looking at the correlation color matrix we can say that defaulters are highly correlated with bank balance.
```{r}
library(corrplot)
corrplot(cor(loan_data[c('credit.policy','int.rate','installment','log.annual.inc','dti','fico','not.fully.paid','pub.rec')], method = c("spearman")))
```
### From the correlation matrix above there represents the correlation visually, shows not of the attributes have affect on not.fully.paid i.e. defualter.
```{r}
library(corrplot)
corrplot(cor(application_data[c('AMT_INCOME_TOTAL','AMT_CREDIT','AMT_ANNUITY','AMT_GOODS_PRICE','DAYS_BIRTH','DAYS_EMPLOYED','TARGET')], method = c("spearman")))
```
### none of the attributes selected have direct affect on Target fields.

### For further steps I will analyze income and loan defaulter to some insight.
### Also I am planning to fit a logistic regression model on defaulter as dependent variable and employment, annual salary and bank-balance as independent variables.
### I will also do some further analysis on fico and interest rate.